---
title: "Homework 6"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(viridis)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 2

## Load & Clean Data

1. Load data
2. Create following variables:
   * city_state
   * case_solved: binary variable where 0 = case unresolved, 1 = case resolved
3. Filter the data in the following ways:
   * For city_state, remove Dallax, TX; Phoenix, AZ; Kansas City, MO; Tulsa, AL
   * For victim_race, only includ White & Black
5. Convert victim_age's data type from char to numeric
6. Skim
```{r data_clean}
homicide_df = read.csv('data/homicide.csv') %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         case_solved = as.numeric(case_when(
           disposition == "Closed without arrest" ~ "0",
           disposition == "Open/No arrest" ~ "0",
           disposition == "Closed by arrest" ~ "1"))) %>% 
  filter(city_state != "Dallas, TX", 
         city_state != "Phoenix, AZ", 
         city_state != "Kansas City, MO", 
         city_state != "Tulsa, AL", 
         victim_race %in% c("White" ,"Black")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```

```{r skim, include = FALSE}
skimr::skim(homicide_df)
```


## Baltimore, MD: GLM

1. Create a new data frame called "baltimore_df"
```{r baltimore_df}
homicide_baltimore = homicide_df %>% 
  filter(city_state == "Baltimore, MD")
```

2. Fit a log reg (outcome = case_solved, predictors = age, sex, race)
3. Save glm output
4. Find CI & estimate for odds ratio for male vs. female (victim_sexMale row) while keeping all other var
```{r glm}
baltimore_log_fit = 
  homicide_baltimore %>% 
  glm(case_solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

summary(baltimore_log_fit)

baltimore_log_fit %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         OR_CI_lower = exp(estimate - 1.96*(std.error)),
         OR_CI_upper = exp(estimate + 1.96*(std.error))) %>% 
  select(term, log_OR = estimate, OR, OR_CI_lower, OR_CI_upper, p.value) %>% 
  knitr::kable()
```

## GLM for Each City

Run the test for all cities & find OR, including 95% CI
```{r glm_all}
homicide_df %>% 
  glm(case_solved ~ victim_age + victim_race + victim_sex, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

homicide_df %>% 
  group_by(city_state) %>% 
  summarise(total = n())

homicide_log_fit =
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(case_solved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)) %>% 
  unnest(results) %>% 
    filter(term == "victim_sexMale") %>% 
    mutate(OR = exp(estimate),
           OR_CI_lower = exp(estimate - 1.96*(std.error)),
           OR_CI_upper = exp(estimate + 1.96*(std.error))) %>%
    select(city_state, OR, OR_CI_lower, OR_CI_upper)

knitr::kable(homicide_log_fit)
```

## Plot Resolved Homicide Cases in Each City (Male vs. Female)

```{r plot}
homicide_plot = homicide_log_fit %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(
    title = "OR for Solving Homicide Cases in the US (Male vs. Female Victims)",
    x = "Location (city, state)",
    y = "Adjusted OR")

homicide_plot
```

This plot displays estimated ORs and CIs for solving homicide cases in each city. Based on the plot, the odds of resolving homicides with female vs. male plot based on city, state can be summarized as follows:  
Cities with nearly equal odds ratio (OR =~ 1):  
* Atlanta, GA  
* Richmond, VA  
Cities where OR, male > OR, female (OR > 1):  
* Nashville, TN  
* Fresno, CA  
* Stockton, CA  
* Albuquerque, NM  
For all other cities, the odds of solving homicide cases with female victim is higher than the odds of solving homicide cases with male victims.

# Problem 3

## Load, Clean, and Observe Data

1. Load data
2. For categorical variables, convert the data type from numeric to factor
3. Rename variables (for future model)
```{r}
bw_df = read.csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex), 
         frace = as.factor(frace), 
         malform = as.factor(malform), 
         mrace = as.factor(mrace)) %>% 
  rename(gest_age = gaweeks,
         mom_bmi = ppbmi,
         mom_age = momage,
         n_cig = smoken)
```

3. Checkign for NA
```{r}
skimr::skim(bw_df)
```
No missing values per output

## Testing Variables for the Model

I would like to propose the following model:  
* Outcome: birth weight (bwt)
* Predictors: gestational age (gest_age), mom's pre-pregnancy BMI (mom_bmi), avg # of cigarettes smoked per day during pregnancy (n_cig), and weight gain during pregnancy (wtgain) 
I am interested observing maternal health behavior and early vs. full-term pregnancy's impact birth weight. 

1. Used glance with full model vs. reduced models to decided which predictors should be kept vs. removed
2. Reduced Model #1: When pre-pregnancy BMI was removed, both AIC & BIC increased. So, decided to keep pre-pregnancy BMI
3. Reduced Model #2: When weight gain during pregnancy (lb) was removed, AIC & BIC increased. Hence, also decided to keep this variable.
4. Decided to proceed with the full model
```{r}
bw_full = bw_df %>% 
  lm(bwt ~ gest_age + mom_bmi + n_cig + wtgain, data = .)

bw_full %>% 
  broom::glance()

bw_red1 = bw_df %>% 
  lm(bwt ~ gest_age + n_cig + wtgain, data = .)

bw_red1 %>% 
  broom::glance()

bw_red2 = bw_df %>% 
  lm(bwt ~ gest_age + mom_bmi + n_cig, data = .)

bw_red2 %>% 
  broom::glance()
```

Used tidy for a quick summary of the model
```{r}
bw_full %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```


## Plot of Model Residuals Against Fitted Values

```{r}
plot1 = bw_df %>% 
  modelr::add_residuals(bw_full) %>% 
  modelr::add_predictions(bw_full) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    title = "Residuals vs. Fitted Values",
    x = "Fitted Values",
    y = "Residuals")

plot1
```

## Compare Models: Model 2

